Response to the defense feedback

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Method}
In this section, we first provide two examples that show how we rank the side-channel vulnerability. After that, we prove that our method is a conservative estimate of the amount of each leakage.

@@

With THEOREM~\ref{the1}, we can have
\begin{align*}
  \max_{p(k)} H |O| >= \max_{p(k')} H |O'| >= H |O'|
\end{align*}

@@

\section{Align Address Access Across Multiple Executions}
We compare address accesses of different executions generated by different inputs to quantify the amount of leakage information. A meaningful comparison requires that we align executions across multiple runs before we quantify the leakage. In this work, we combine the information from both the source code and the binary executable to align the memory access during the execution.

@@

Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$). If the value of index ($i$) is associated with secret information, the example is vulnerable to side-channel attacks. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated at different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800} and \textsf{T} is allocated at the address \texttt{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}) so we get two different memory accesses. Under the circumstance, it is a false positive. Without proper alignment, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different indexes. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} cannot observe the difference here, which is a false positive.

\textbf{Our Strategy: } We assign a value for each memory location~\cite{sumner2010memory}. The value should satisfy the following characteristics.
\begin{itemize}
  \item \textbf{Uniqueness.} At any point during the execution, different memory cells must have a different value.
  \item \textbf{Alignment.} The same memory cell across multiple executions should share the same value.
\end{itemize}

@@

\textbf{Run-time Information.} One example here is the concrete memory address during the runtime. Such a value satisfies the uniqueness characteristic. However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.

>>>>

\section{Method}\label{chapter5:method}
In this section, we first provide two examples that show how we rank the side-channel vulnerability. After that, we prove that our method is a conservative estimate of the amount of each leakage.

@@

With Theorem~\ref{the1}, we can have
\begin{align*}
  \max_{p(k)} H |O| >= \max_{p(k')} H |O'| >= H |O'|
\end{align*}

@@

\section{Align Address Access Across Multiple Executions}
We compare the address accesses of different executions generated by different inputs to quantify the amount of leakage information. A meaningful comparison requires that we align executions across multiple runs before we quantify the leakage. In this work, we combine the information from both the source code and the binary executable to align the memory access during the execution.

@@

Considering the example in Figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$). If the value of index ($i$) is associated with the secret information, the example is vulnerable to side-channel attacks. Unlike the example in Section~\ref{chapter5:method}, the array \textsf{T} is on the heap. Data on the heap are often allocated at different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800}, and \textsf{T} is allocated at the address \texttt{0xff124801} during the second run. For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, the base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}) so we get two different memory accesses. Under the circumstance, it is a false positive. Without proper alignment, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different indexes. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} cannot observe the difference here, which is a false positive.

\subsubsection*{Our Strategy} We assign a value for each memory location~\cite{sumner2010memory}. The value should satisfy the following characteristics.
\begin{itemize}
  \item \textbf{Uniqueness.} At any point during the execution, different memory cells must have a different value.
  \item \textbf{Alignment.} The same memory cell across multiple executions should share the same value.
\end{itemize}

@@

\textbf{Runtime Information.} One example here is the concrete memory address during execution. Such a value satisfies the uniqueness characteristic. However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.
